**Density Dependence**

### 2023-02-20 Rmd/mseMac.Rmd
with SRR

opts_chunk$set(cache     =TRUE, 
               comment   =NA, 
               warning   =FALSE, 
               message   =FALSE, 
               error     =FALSE, 
               echo      =FALSE, 
               eval      =TRUE,cache   =TRUE,
               cache.path="../cache/mse/",
               fig.path  ="../tex/figs/mse/",
               fig.width =8,
               fig.height=6,
               dev       ="png")

@@

```{r, pars}
par=FLPar(c(m1=0.15/(0.2^-0.288),m2=-0.28,bref=NA,b=0.3,matk=30.1, w50=0.2))
```

@@

```{r,eq}
sr=fmle(as.FLSR(iter(vpa,1),model="bevholt"),control=list(silent=TRUE))
eq=FLBRP(iter(vpa,1),sr=sr)
```

@@

@@

>>>>

opts_chunk$set(cache     =TRUE, 
               comment   =NA, 
               warning   =FALSE, 
               message   =FALSE, 
               error     =FALSE, 
               echo      =FALSE, 
               eval      =TRUE,cache   =TRUE,
               cache.path="../cache/mseMac/",
               fig.path  ="../tex/figs/mseMac/",
               fig.width =8,
               fig.height=6,
               dev       ="png")

@@

```{r, pars}
par=FLPar(c(m1=0.15/(0.2^-0.288),m2=-0.288,bref=NA,b=0.3,matk=30.1,w50=0.2))
```

@@

```{r,eq}
sr=fmle(as.FLSR(iter(stk,1),model="bevholt"),control=list(silent=TRUE))
eq=FLBRP(iter(vpa,1),sr=sr)
```

@@

```{r}
save(oms,file="~/Desktop/tmp/oms.RData")
```

@@

```{r}
load("/home/laurie/Dropbox/pelagics/results/mac/figures/mac_objects.RData")

dt1=model.frame(FLQuants("Rec"=rec(oms[[1]][,"2050"]),"SSB"=ssb(oms[[1]][,"2050"])),drop=T)
dt2=model.frame(FLQuants("Rec"=rec(vpa[,"2050"]),"SSB"=ssb(vpa[,"2050"])),drop=T)

ggplot()+
  geom_line(aes(SSB,Rec),data=dt1)+
  geom_line(aes(SSB,Rec),data=dt2)
```

```{r}
stk=window(iter(vpa,1),end=2019)
sr=fmle(as.FLSR(stk,model="bevholtSV"),fixed=list(s=0.8,spr0=mean(spr0(stk))),
                control=list(silent=TRUE))
eq=FLBRP(stk,sr=ab(sr))

stk=window(iter(vpaM,1),end=2019)
srM=fmle(as.FLSR(stk,model="bevholtSV"),fixed=list(s=0.8,spr0=mean(spr0(stk))),
                control=list(silent=TRUE))
eqM=FLBRP(stk,sr=ab(srM))

stk=window(iter(vpaDDM,1),end=2019)
srDDM=fmle(as.FLSR(stk,model="bevholtSV"),fixed=list(s=0.8,spr0=mean(spr0(stk))),
                control=list(silent=TRUE))
eqDDM=FLBRP(stk,sr=ab(srDDM))

stk=window(iter(vpaDDMM,1),end=2019)
srDDMM=fmle(as.FLSR(stk,model="bevholtSV"),fixed=list(s=0.8,spr0=mean(spr0(stk))),
                control=list(silent=TRUE))
eqDDMM=FLBRP(stk,sr=ab(srDDMM))

stk=window(iter(vpaDDMMM,1),end=2019)
srDDMM=fmle(as.FLSR(stk,model="bevholtSV"),fixed=list(s=0.8,spr0=mean(spr0(stk))),
                control=list(silent=TRUE))
eqDDMMM=FLBRP(stk,sr=ab(srDDMMM))

dat=rbind(
  cbind(What="ICES",    model.frame(FLQuants(eq,rec=rec,ssb=ssb,catch=catch),drop=T)),
  cbind(What="VPA",     model.frame(FLQuants(eqM,rec=rec,ssb=ssb,catch=catch),drop=T)),
  cbind(What="VPA M",   model.frame(FLQuants(eqDDM,rec=rec,ssb=ssb,catch=catch),drop=T)),
  cbind(What="VPA MM",  model.frame(FLQuants(eqDDMM,rec=rec,ssb=ssb,catch=catch),drop=T)),
  cbind(What="VPA MMM", model.frame(FLQuants(eqDDMMM,rec=rec,ssb=ssb,catch=catch),drop=T)))

ggplot(dat)+
  geom_line(aes(ssb,catch,col=What))

ggplot(dat)+
  geom_line(aes(ssb,rec,col=What))

```
